Network Cascades

### 2016-08-25 paper/paper.tex
Do some minor improvements

\section{Cascade Condition}\label{sec:section}

@@

\begin{itemize}
  \item $\sum_{k=0}^\infty$: We iterate over all possible thresholds $k$ from $0$ to infinity. The sum converges and in reality it is possible to only calculate the ``first few'' elements
  \item $k (k-1)$ Nevermind that. These are remainders of the generating functions black magic.
  \item $\rho_k$ The probability that a node with degree k is vulerable (according to a probability distribution)
  \item $p_k$ The probability that a node has the threshold $k$ (according to a probability distribution)
\end{itemize}

@@

The mathematical basis for the calculations in section \ref{sec:cascade-condition} about the cascade condition is formed by genrating functions (hence the name $G_0''(1)$ for the condition). Generating functions are a convenient tool to express series of numbers in a concise fashion. Applied to propability distributions, they allow for a convenient examination of that distribution.

>>>>

\section{Analysis of the Model}\label{sec:analysis}

@@

\begin{itemize}
  \item $\sum_{k=0}^\infty$: We iterate over all possible thresholds $k$ from $0$ to infinity. The sum converges and in reality it is possible to only calculate the ``first few'' elements
  \item $k (k-1)$ Nevermind that. These are remainders of the generating functions black magic.
  \item $\rho_k$ The probability that a node with degree k is vulerable (according to a probability distribution)
  \item $p_k$ The probability that a node has the threshold $k$ (according to a probability distribution)
  \item $G_0''(1)$ Treat this as an alias for the sum term. It is actually the solution for $x = 1$ of the second derivative of the generating function for the distribution of vulnerable nodes (which is $G_0(x) = \sum_k \rho_kp_kx^k$; the derivative-relationship is clearly visible)
\end{itemize}

@@

The mathematical basis for the calculations in section \ref{sec:analysis} about the cascade condition is formed by genrating functions (hence the name $G_0''(1)$ for the condition). Generating functions are a convenient tool to express series of numbers in a concise fashion. Applied to propability distributions, they allow for a convenient examination of that distribution.
